Models

### 2023-05-11 Code/Models.Rmd
Identity vs log comparison is in the bottom 4 chunks.  For each dataset the link=identity was compared with link=log

```{r}
set.seed(1)
simulation <- function(model, base){
    simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
  }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < 0.1))
  print(quantile(x, prob = c(.00001, .0001, .0005, .001)))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
}
simulation(old_pooled_year_gamma_log, old_pooled_one_gamma_log)
```

@@

```{r}
library(xtable)
xtable(men_pooled_year_gamma_log)
```
```{r}
library(memisc)
mtable(men_pooled_year_gamma_log)
```

>>>>

```{r}
set.seed(1)
simulation <- function(model, base){
    simfit <- function(model, n = 10000000) {
    vc <- as.data.frame(VarCorr(model))
    ## mu <- exp(coef(model)$Year[,]) ## using fitted random effects only
    z <- rnorm(n, sd = vc$sdcor[1]) #$ using generated random effects
    mu <- exp(fixef(model) + z)
    shape <- 1 / vc$vcov[2]
    x <- rgamma(n, shape = shape, scale = mu / shape)
    x
    }
  sbase <- summary(base)
  #print(sbase)
  x <- simfit(model)
  print(mean(x < 0.08))
  print(quantile(x, prob = c(.00001, .0001, .0005, .001)))
  ## compare with and without random effect
  plot(density(x)) # with random effect
  curve(dgamma(x, shape = 1 / sbase$dispersion, 
               scale = exp(coef(base)) * sbase$dispersion), 
        0.08, 0.22, add = TRUE, col = "blue") # fixed effect only
}
simulation(old_pooled_year_gamma_log, old_pooled_one_gamma_log)
```

@@

#Trying out identity link
```{r}
men_finals_year_gamma_log <- glmer(RxnTime ~ (1|Year), data = men_finals, family = Gamma(link = "log"))
t1 <- glmer(RxnTime ~ (1|Year), data = men_finals, family = Gamma(link = "identity"))
paste("Gamma and log with year effect has AIC of", AIC(men_finals_year_gamma_log), "and log-lik of", logLik(men_finals_year_gamma_log))
paste("Linear without year effect has AIC of", AIC(t1), "and log-lik of", logLik(t1))
```

```{r}
men_old_finals_year_gamma_log <- glmer(RxnTime ~ (1|Year), data = men_old_finals, family = Gamma(link = "log"))
t2 <- glmer(RxnTime ~ (1|Year), data = men_old_finals, family = Gamma(link = "identity"))
paste("Linear without year effect has AIC of", AIC(men_old_finals_year_gamma_log), "and log-lik of", logLik(men_old_finals_year_gamma_log))
paste("Linear without year effect has AIC of", AIC(t2), "and log-lik of", logLik(t2))
```

```{r}
men_pooled_year_gamma_log <- glmer(RxnTime ~ (1|Year), data = men_pooled, family = Gamma(link = "log"))
t3 <- glmer(RxnTime ~ (1|Year), data = men_pooled, family = Gamma(link = "identity"))
paste("Gamma and log with year effect has AIC of", AIC(men_pooled_year_gamma_log), "and log-lik of", logLik(men_pooled_year_gamma_log))
paste("Linear without year effect has AIC of", AIC(t3), "and log-lik of", logLik(t3))
```

```{r}
men_old_pooled_year_gamma_log <- glmer(RxnTime ~ (1|Year), data = men_old_pooled, family = Gamma(link = "log"))
t4 <- glmer(RxnTime ~ (1|Year), data = men_old_pooled, family = Gamma(link = "identity"))
paste("Gamma and log with year effect has AIC of", AIC(men_old_pooled_year_gamma_log), "and log-lik of", logLik(men_old_pooled_year_gamma_log))
paste("Linear without year effect has AIC of", AIC(t4), "and log-lik of", logLik(t4))
